\documentclass[10pt,a4paper]{article}

% =========================
% PAGE / MARGINS (balanced for 2 pages)
% =========================
\usepackage[a4paper,top=0.45in,bottom=0.45in,left=0.45in,right=0.45in]{geometry}

% =========================
% FONTS (pdfLaTeX, no imports)
% =========================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{sourcesanspro}

% =========================
% CORE
% =========================
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{needspace}
\usepackage{paracol}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[none]{hyphenat} % prevents word hyphenation/breaking

% =========================
% COLORS
% =========================
\definecolor{primary}{HTML}{111827}
\definecolor{secondary}{HTML}{6B7280}
\definecolor{rulecolor}{HTML}{E5E7EB}

% =========================
% LINKS (ATS-safe)
% =========================
\hypersetup{
  colorlinks=true,
  linkcolor=primary,
  urlcolor=primary,
  citecolor=primary,
  pdfborder={0 0 0}
}
\urlstyle{same}

% =========================
% TYPOGRAPHY
% =========================
\setlength{\headheight}{30pt}
\setlength{\headsep}{5pt}
\setlength{\columnsep}{1.8em} 
\RaggedRight
\linespread{1.03}
\setlength{\emergencystretch}{2em}
\sloppy

% =========================
% PAGE HEADER (PAGE 1 / PAGE 2)
% =========================
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\textcolor{secondary}{\footnotesize PAGE \thepage}}

% =========================
% SECTION STYLE (RIGHT COLUMN)
% =========================
\titleformat{\section}
  {\needspace{3\baselineskip}\large\bfseries\color{primary}}
  {}
  {0pt}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{0pt}{4pt}

% =========================
% LISTS
% =========================
\setlist[itemize]{leftmargin=1.15em, itemsep=2pt, topsep=3pt, parsep=0pt, partopsep=0pt}
\renewcommand\labelitemi{\textbullet}

% =========================
% SIZING HELPERS (font hierarchy)
% =========================
\newcommand{\NameSize}{\fontsize{22}{24}\selectfont}
\newcommand{\TitleSize}{\fontsize{10.8}{13}\selectfont}
\newcommand{\TagSize}{\fontsize{10}{12}\selectfont}
\newcommand{\BodySize}{\fontsize{9.7}{12}\selectfont}
\newcommand{\SmallBody}{\fontsize{9.2}{11.4}\selectfont}

% =========================
% DIVIDERS
% =========================
\newcommand{\topdivider}{\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{0pt}}
\newcommand{\blockdivider}{\vspace{0pt}\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{4pt}}

% =========================
% SIDEBAR MACROS (LEFT COLUMN)
% All right-aligned, like your screenshots
% =========================
\newcommand{\sideheading}[1]{%
  {\RaggedLeft\bfseries\color{primary}\large\MakeUppercase{#1}\par}%
  \vspace{0pt}%
}
\newcommand{\sidesub}[1]{%
  \vspace{6pt}%
  {\RaggedLeft\bfseries\color{primary}\MakeUppercase{#1}\par}%
  \vspace{3pt}%
}
\newcommand{\sideitem}[1]{%
  {\RaggedLeft\SmallBody\textcolor{primary}{%
    \hyphenpenalty=10000\exhyphenpenalty=10000 #1}\par}%
}
% =========================
% RIGHT COLUMN HELPERS
% =========================
\newcommand{\roleheader}[4]{%
  \textbf{\MakeUppercase{#1}} \hfill \textcolor{primary}{#2}\\
  \textbf{\MakeUppercase{#3}} \hfill \textcolor{primary}{#4}\\[4pt]
}
\newcommand{\projecttitle}[1]{\textbf{#1}\par\vspace{2pt}}

% =========================
% DOCUMENT
% =========================
\begin{document}
\BodySize

% =========================
% PAGE 1 HEADER (centered)
% =========================
\begin{center}
{\NameSize \bfseries JAKIR HUSSAIN}\\[4pt]
{\TitleSize \bfseries SENIOR FULL-STACK ENGINEER}\\[2pt]
{\TagSize \bfseries NODE JS \;|\; AI PLATFORMS \;|\; CLOUD \& APIs}\\[6pt]

\SmallBody
Senior Full-Stack Engineer with 8+ years of experience designing and delivering cloud-native, AI-integrated platforms using Node.js, React, and GraphQL. Specialized in microservice architectures, CI/CD automation, and cloud deployments on AWS and Kubernetes, with strong exposure to agentic AI systems, RAG pipelines, and enterprise APIs.\\[5pt]
Recognized for effectively bridging frontend UX excellence with backend scalability and performance, delivering secure, resilient, and data-intensive platforms across fintech, media, and regulated enterprise environments.\\[8pt]

\href{mailto:itsjakirhussain@gmail.com}{itsjakirhussain@gmail.com} \;|\;
+971 551419969 \;|\;
Dubai, UAE \;|\;
\href{https://linkedin.com/in/iam-hussain}{linkedin.com/in/iam-hussain} \;|\;
\href{https://iam-hussain.site}{iam-hussain.site}

\end{center}
\vspace{-8pt}
\topdivider
\vspace{2pt}
% ============================================================
% PAGE 1: LEFT = SKILLS, RIGHT = SYNECHRON
% ============================================================
\setcolumnwidth{0.31\textwidth,0.69\textwidth}
\begin{paracol}{2}

% ---------- LEFT COLUMN ----------
\switchcolumn[0]*
\sideheading{Skills}

\sidesub{Back-End \& APIs}
\sideitem{Node.js, Bun}
\sideitem{TypeScript, JavaScript}
\sideitem{Express.js, Hapi}
\sideitem{REST APIs, GraphQL}
\sideitem{Apollo GraphQL, GraphQL Modules}
\sideitem{Prisma ORM, Sequelize ORM}

\sidesub{Front-End}
\sideitem{React.js, Next.js}
\sideitem{Redux Toolkit, React Query, React Router}
\sideitem{Tailwind CSS, Material UI}
\sideitem{Styled Components}
\sideitem{Vite, Webpack, Babel}
\sideitem{Storybook}
\sideitem{Framer Motion}

\sidesub{Mobile \& Desktop}
\sideitem{React Native, Expo}
\sideitem{Electron, Tauri}
\sideitem{React Native WebView}

\sidesub{AI \& LLM Engineering}
\sideitem{LLM Application Development}
\sideitem{Multi-Agent Architectures \& Tool Calling}
\sideitem{LangChain (Agents, Tools)}
\sideitem{OpenAI (ChatGPT), LLaMA, Claude}
\sideitem{Prompt Engineering \& Safety}
\sideitem{RAG, AI Guardrails \& Validation}

\sidesub{Data, Caching \& Search}
\sideitem{MongoDB, PostgreSQL}
\sideitem{MySQL, DynamoDB}
\sideitem{Redis (Embedded \& Distributed)}
\sideitem{Elasticsearch}

\sidesub{Cloud, DevOps \& Platform}
\sideitem{AWS (Lambda, S3)}
\sideitem{Docker, Podman}
\sideitem{Kubernetes, OpenShift}
\sideitem{Terraform}
\sideitem{Jenkins, GitHub Actions}
\sideitem{Serverless Architectures}
\sideitem{Load Balancers, CDN}

\sidesub{Testing \& QA}
\sideitem{Playwright, Cypress}
\sideitem{Jest, Mocha, Chai}
\sideitem{Cucumber.js}
\sideitem{Vitest}

\vspace{16pt}

\sidesub{Engineering Practices}
\sideitem{System Design \& Architecture}
\sideitem{Microservices Architecture}
\sideitem{Performance Optimization}
\sideitem{Security-Aware Development}
\sideitem{Compliance-Driven Systems}
\sideitem{CI/CD Automation}
\sideitem{Web Accessibility (WCAG)}

\vspace{10pt}
\sidesub{Freelance / Contract}
\vspace{4pt}

\sideitem{\textbf{Origin Protocol}}
\sideitem{Frontend Engineer — Remote}
\sideitem{Dec 2020 -- Feb 2021}

\vspace{3pt}
\sideitem{Worked on an Ethereum-based dApp, implementing Web3.js and MetaMask wallet integration. Collaborated on GraphQL API extensions within a Lerna-managed monorepo.}

\vspace{8pt}

\sideitem{\textbf{Threado}}
\sideitem{Frontend Engineer — Bangalore, India}
\sideitem{Nov 2021 -- Jan 2022}

\vspace{3pt}
\sideitem{Contributed to a community management web application using TypeScript, React, and Next.js with a component-driven UI approach.}

\vspace{10pt}

\sidesub{Early Career}

\sideitem{\textbf{Selsun Technologies}}
\sideitem{Software Trainee — Chennai, India}
\sideitem{Dec 2017 -- Nov 2018}

\vspace{3pt}
\sideitem{Developed computer vision solutions for semi-automated equipment, enhancing OpenCV-based image processing algorithms using C++ and Python.}

\vspace{10pt}

\sideheading{Education}
\vspace{4pt}
\sideitem{\textbf{Arunai Engineering College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Bachelor of Engineering in Mechanical Engineering}
\sideitem{Aug 2013 -- Jun 2016}

\vspace{8pt}
\sideitem{\textbf{Kumaran Polytechnic College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Diploma in Mechanical Engineering}
\sideitem{Aug 2010 -- Jun 2013}

\vspace{10pt}
\sidesub{Languages}
\sideitem{ENGLISH, TAMIL, HINDI}

\vspace{10pt}
\sidesub{Social}

\sideitem{Portfolio — \href{https://iam-hussain.site}{iam-hussain.site}}
\sideitem{LinkedIn — \href{https://linkedin.com/in/iam-hussain}{iam-hussain}}
\sideitem{GitHub — \href{https://github.com/iam-hussain}{iam-hussain}}

% ---------- RIGHT COLUMN ----------
\switchcolumn[1]
\section*{Experience}
\roleheader{Synechron Technologies LLC}{Dubai, UAE}{Lead -- Technology}{Dec 2024 -- Present}

\projecttitle{Treasury AI Assistant -- Emirates NBD}
Leading the design and delivery of an AI-powered conversational assistant for the Treasury department, enabling real-time insights, operational intelligence, and decision support within a highly regulated banking environment.

\begin{itemize}
  \item Architected a \textbf{multi-agent LLM system} with deterministic orchestration, domain reasoning, tool execution, and response validation to ensure auditable and traceable AI outputs.
  \item Designed secure \textbf{prompt and tool workflows} enabling controlled interaction with \textbf{Calypso APIs}, enforcing strict access controls and data boundaries.
  \item Implemented \textbf{agentic AI patterns} using \textbf{LangChain and LangGraph}, supporting controlled execution, failure isolation, and observability.
  \item Built \textbf{Retrieval-Augmented Generation (RAG)} pipelines using vector databases and embeddings to deliver context-aware responses while preventing data leakage.
  \item Implemented \textbf{Redis-based contextual memory and caching} for session-level state management and low-latency retrieval.
  \item Integrated multiple LLM providers (\textbf{OpenAI, LLaMA, Claude}) with routing, fallback strategies, and sensitivity-aware response handling.
  \item Established enterprise-grade \textbf{AI guardrails} covering prompt safety, authorization, data masking, and compliance validation.
  \item Collaborated with treasury, risk, compliance, and security teams to align with banking governance and prepare the platform for production rollout.
\end{itemize}

\textbf{Tech Stack} \\
Node.js, TypeScript, LangChain, LangGraph, Multi-Agent LLM Architectures, Agentic AI, RAG, Vector Databases, OpenAI, LLaMA, Claude, Redis, Calypso APIs

\blockdivider

\projecttitle{Open Finance Platform -- Emirates NBD}
Led backend and API architecture for Emirates NBD’s Open Finance Platform under the UAE Central Bank \textbf{``Compete \& Comply''} Open Banking framework.

\begin{itemize}
  \item Designed and delivered \textbf{Node.js / TypeScript microservices} enabling secure, consent-driven data exchange between Licensed Financial Institutions (LFIs) and Third-Party Providers (TPPs).
  \item Implemented \textbf{REST and GraphQL APIs}, integrated with React and Next.js dashboards for regulatory workflows and consent lifecycle management.
  \item Implemented \textbf{3Scale API Gateway} and automated \textbf{CI/CD pipelines} (Jenkins, OpenShift), reducing release cycles by approximately \textbf{40\%}.
  \item Worked directly with UAE Central Bank regulators to ensure compliance with Open Banking standards, data governance, and security controls.
  \item Partnered with AI and analytics teams to prototype \textbf{predictive consent analytics} and anomaly detection dashboards.
\end{itemize}

\textbf{Tech Stack} \\
Express.js, TypeScript, REST, GraphQL, React.js, Material UI, MongoDB, OpenShift, 3Scale, Docker, Kubernetes, Jenkins, Playwright, Cucumber.js


\vspace{16pt}

\roleheader{Condé Nast Technology Lab}{Bangalore, India}{Software Engineer II}{Jun 2021 -- Nov 2024}

\projecttitle{The New Yorker -- Caption Contest, AI Personalization, Home, Quizzes \& Newsletters}
\begin{itemize}
  \item Architected and delivered a \textbf{full-stack AI personalization platform} integrating ML-driven recommendations with real-time React rendering.
  \item Built adaptive \textbf{React and Next.js experiences} backed by personalization APIs, increasing user engagement by \textbf{27\%}.
  \item Designed and automated \textbf{Kubernetes CronJobs} for large-scale Instagram caption ingestion, enabling continuous content synchronization.
  \item Converted predictive analytics into interactive UI components and scalable \textbf{GraphQL APIs} in collaboration with ML and backend teams.
  \item Led the POC and production rollout of \textbf{server-driven UI}, reducing duplicated layout logic by \textbf{40\%}.
  \item Developed the \textbf{``Name Drop''} quiz application end-to-end from Figma designs, combining backend logic, animation-driven UX, and performance optimization.
  \item Improved homepage accessibility through audio-article playback and adaptive media handling.
  \item Optimized newsletter subscription workflows, increasing recurring user sign-ups by \textbf{18\%}.
  \item Mentored engineers on React performance optimization, memoization, and accessibility best practices.
  \item Implemented end-to-end analytics pipelines (\textbf{Snowplow + GraphQL}) to support AI-driven personalization feedback loops.
\end{itemize}

\textbf{Tech Stack} \\
React.js, Next.js, TypeScript, GraphQL, Node.js, Styled Components, Storybook, Prisma, MongoDB, MySQL, Kubernetes, Terraform, GitHub Actions, AWS, Hapi, Express, Datadog, Serverless Framework, Fastly CDN, Databricks, Vitest

\blockdivider

\roleheader{HTC Global Services}{Chennai, Tamil Nadu, India}{Software Developer}{Feb 2020 -- Jun 2021}

\projecttitle{Manipal Education and Lead Management}
\begin{itemize}
  \item Designed and built microservice-based APIs for Manipal University’s online platform serving 50K+ students.
  \item Implemented serverless ingestion pipelines (AWS Lambda, SQS, DynamoDB) to process Salesforce data 60\% faster.
  \item Integrated Elasticsearch search and asynchronous event processing to enable real-time analytics and reporting.
  \item Deployed Dockerized Node.js services on AWS EC2, improving CI/CD reliability by \textasciitilde30\%.
  \item Collaborated closely with frontend teams to integrate React applications with backend services.
\end{itemize}

\textbf{Tech Stack} \\
Node.js, Express.js, TypeScript, Sequelize, DynamoDB, Elasticsearch, AWS Lambda, SQS, Docker

\blockdivider

\roleheader{Develop Script LLC}{Chennai, Tamil Nadu, India}{Node JS Developer}{Dec 2018 -- Jan 2020}

\projecttitle{Mazzady, Sothebi, PreRio, SlotCycle}
\begin{itemize}
  \item Built real-time auction platforms using Node.js, Express, and WebSockets (Socket.IO).
  \item Implemented Redis Pub/Sub for low-latency bid synchronization across concurrent users.
  \item Integrated payments, logistics, and notifications to deliver end-to-end e-commerce workflows.
  \item Developed React-based admin and bidding interfaces with real-time updates.
\end{itemize}

\textbf{Tech Stack} \\
Node.js, Express.js, React.js, Socket.IO, Redis, AWS RDS, MySQL

\end{paracol}

\end{document}