\documentclass[10pt,a4paper]{article}

% =========================
% PAGE / MARGINS (balanced for 2 pages)
% =========================
\usepackage[a4paper,top=0.45in,bottom=0.45in,left=0.45in,right=0.45in]{geometry}

% =========================
% FONTS (pdfLaTeX, no imports)
% =========================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{sourcesanspro}

% =========================
% CORE
% =========================
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{needspace}
\usepackage{paracol}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[none]{hyphenat} % prevents word hyphenation/breaking

% =========================
% COLORS
% =========================
\definecolor{primary}{HTML}{111827}
\definecolor{secondary}{HTML}{6B7280}
\definecolor{rulecolor}{HTML}{E5E7EB}

% =========================
% LINKS (ATS-safe)
% =========================
\hypersetup{
  colorlinks=true,
  linkcolor=primary,
  urlcolor=primary,
  citecolor=primary,
  pdfborder={0 0 0}
}
\urlstyle{same}

% =========================
% TYPOGRAPHY
% =========================
\setlength{\headheight}{30pt}
\setlength{\headsep}{5pt}
\setlength{\columnsep}{1.8em}
\RaggedRight
\linespread{1.03}
\setlength{\emergencystretch}{2em}
\sloppy

% =========================
% PAGE HEADER (PAGE 1 / PAGE 2)
% =========================
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\textcolor{secondary}{\footnotesize PAGE \thepage}}

% =========================
% SECTION STYLE (RIGHT COLUMN)
% =========================
\titleformat{\section}
  {\needspace{3\baselineskip}\large\bfseries\color{primary}}
  {}
  {0pt}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{0pt}{4pt}

% =========================
% LISTS
% =========================
\setlist[itemize]{leftmargin=1.15em, itemsep=2pt, topsep=3pt, parsep=0pt, partopsep=0pt}
\renewcommand\labelitemi{\textbullet}

% =========================
% SIZING HELPERS (font hierarchy)
% =========================
\newcommand{\NameSize}{\fontsize{22}{24}\selectfont}
\newcommand{\TitleSize}{\fontsize{10.8}{13}\selectfont}
\newcommand{\TagSize}{\fontsize{10}{12}\selectfont}
\newcommand{\BodySize}{\fontsize{9.7}{12}\selectfont}
\newcommand{\SmallBody}{\fontsize{9.2}{11.4}\selectfont}

% =========================
% DIVIDERS
% =========================
\newcommand{\topdivider}{\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{0pt}}
\newcommand{\blockdivider}{\vspace{0pt}\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{4pt}}

% =========================
% SIDEBAR MACROS (LEFT COLUMN)
% =========================
\newcommand{\sideheading}[1]{%
  {\RaggedRight\bfseries\color{primary}\large\MakeUppercase{#1}\par}%
  \vspace{0pt}%
}
\newcommand{\sidesub}[1]{%
  \vspace{6pt}%
  {\RaggedRight\bfseries\color{primary}\MakeUppercase{#1}\par}%
  \vspace{3pt}%
}
\newcommand{\sideitem}[1]{%
  {\RaggedRight\SmallBody\textcolor{primary}{%
    \hyphenpenalty=10000\exhyphenpenalty=10000 #1}\par}%
}

% =========================
% RIGHT COLUMN HELPERS (ATS-optimized role structure)
% =========================
% Order is intentionally: Job Title -> Company | Location -> Dates

% Role header with full-width left/right alignment on both lines
\newcommand{\roleheader}[4]{%
  % Line 1: Job Title — Dates
  \noindent
  \textbf{\MakeUppercase{#3}}%
  \hfill
  \textcolor{secondary}{#4}\\[0pt]

  % Line 2: Company — Location
  \noindent
  \textbf{#1}%
  \hfill
  \textcolor{secondary}{#2}\\[0pt]
}

% Full-width divider under each role header
\newcommand{\roledivider}{%
  \vspace{-1pt}%
  {\color{rulecolor}\rule{\linewidth}{0.5pt}}%
  \vspace{2pt}%
}

% Projects explicitly labeled for ATS parsing
\newcommand{\projecttitle}[1]{\textbf{#1}\par\vspace{2pt}}

% =========================
% DOCUMENT
% =========================
\begin{document}
\BodySize

% =========================
% PAGE 1 HEADER (centered)
% =========================
\begin{center}
{\NameSize \bfseries JAKIR HUSSAIN}\\[4pt]
{\TitleSize \bfseries SENIOR FULL-STACK ENGINEER (FRONTEND-LEANING)}\\[2pt]
{\TagSize \bfseries REACT \;|\; NEXT.JS \;|\; NODE.JS \;|\; AI AGENTS \;|\; CLOUD \& APIs}\\[6pt]

\href{mailto:itsjakirhussain@gmail.com}{itsjakirhussain@gmail.com} \;|\;
+971 551419969 \;|\;
Dubai, UAE \;|\;
\href{https://linkedin.com/in/iam-hussain}{linkedin.com/in/iam-hussain} \;|\;
\href{https://iam-hussain.site}{iam-hussain.site}

\end{center}
\vspace{-8pt}
\topdivider
\vspace{2pt}
\section*{Professional Summary}
\SmallBody
Frontend-leaning Senior Full-Stack Engineer with 8+ years of experience building high-performance, scalable web applications using React, Next.js, and TypeScript, backed by Node.js microservices and GraphQL/REST APIs. Proven expertise in frontend architecture, design systems, server-driven UI, and performance optimization for large-scale platforms.\\[5pt]
Strong exposure to AI-enabled product development, including agentic workflows, tool calling, and Retrieval-Augmented Generation (RAG) to deliver context-aware experiences with governance, safety, and compliance in enterprise environments.\\[8pt]

\vspace{-8pt}
\topdivider
\vspace{2pt}

% ============================================================
% PAGE 1: LEFT = EXPERIENCE, RIGHT = SKILLS
% ============================================================
\setcolumnwidth{0.69\textwidth,0.31\textwidth}
\begin{paracol}{2}

% ---------- LEFT COLUMN ----------
\switchcolumn[0]*
\section*{Work Experience}
\roleheader{Synechron Technologies LLC (Client: Emirates NBD)}{Dubai, UAE}{Lead -- Technology}{Dec 2024 -- Present}
\roledivider

\projecttitle{Project: Treasury AI Assistant - Emirates NBD}
Led the end-to-end engineering of an enterprise-grade AI assistant combining rich frontend experiences, scalable backend services, and agentic AI workflows to deliver real-time treasury insights within a regulated banking environment.

\begin{itemize}
  \item Architected and delivered a \textbf{full-stack AI assistant platform}, combining React-based dashboards with Node.js backend services and multi-agent LLM orchestration.
  \item Owned frontend architecture for complex, data-dense treasury interfaces (search, drill-downs, insights), emphasizing performance, accessibility, and usability.
  \item Designed backend orchestration services in \textbf{Node.js and TypeScript} to coordinate agent execution, tool invocation, and deterministic response flows.
  \item Implemented \textbf{agentic AI patterns} using LangChain and LangGraph, enabling tool calling, retries, validation steps, and controlled execution paths.
  \item Built secure, role-aware UI and API flows integrating LLM responses, backend-calculated metrics, and human-in-the-loop approvals.
  \item Implemented \textbf{RAG pipelines} using vector retrieval to provide context-aware answers while enforcing authorization boundaries and data masking.
  \item Improved end-to-end latency through caching strategies, selective rendering, and \textbf{Redis-backed session memory}.
\end{itemize}

\textbf{Technologies \& Tools}\\
React.js, Next.js, TypeScript, Node.js, LangChain, LangGraph, Multi-Agent LLM Systems, Agentic AI, RAG, Vector Databases, OpenAI, LLaMA, Claude, Redis, Calypso APIs

\blockdivider

\projecttitle{Project: Open Finance Platform - Emirates NBD}
Owned frontend and backend architecture for a consent-driven Open Finance platform under the UAE Central Bank \textbf{``Compete \& Comply''} Open Banking framework.

\begin{itemize}
  \item Led \textbf{full-stack architecture} for Open Finance dashboards and APIs, enabling consent-driven data exchange between Licensed Financial Institutions (LFIs) and Third-Party Providers (TPPs).
  \item Built \textbf{React/Next.js} dashboards for onboarding, consent lifecycle, approvals, and audit workflows using reusable component patterns and form abstractions.
  \item Designed and implemented \textbf{Node.js + TypeScript microservices} exposing REST and GraphQL APIs for consent management, validation rules, audit trails, and reporting.
  \item Standardized API contracts (DTOs, pagination, filtering, error models) to improve frontend reliability, reduce integration defects, and accelerate feature delivery.
  \item Implemented secure authentication/authorization flows (token validation, scope-based access, role permissions) aligned with banking compliance and Open Banking policies.
  \item Integrated \textbf{API gateway policies} and traffic controls (rate limits, throttling, request validation) to enforce secure, predictable, and compliant API behavior.
  \item Improved developer experience and release consistency by aligning frontend components, backend schemas, and CI/CD pipelines across teams.
\end{itemize}

\textbf{Technologies \& Tools}\\
React.js, Next.js, TypeScript, Node.js, REST APIs, GraphQL, Material UI, MongoDB, OpenShift, 3Scale, Docker, Kubernetes, Jenkins, Playwright, Cucumber.js
\vspace{16pt}

\roleheader{Cond\'e Nast Technology Lab}{Bangalore, India}{Software Engineer II}{Jun 2021 -- Nov 2024}
\roledivider

\projecttitle{Project: The New Yorker (Caption Contest, AI Personalization, Home, Quizzes \& Newsletters)}
\begin{itemize}
  \item Led frontend development for high-traffic editorial surfaces at The New Yorker, powering Caption Contest, personalization modules, quizzes, and newsletters.
  \item Architected scalable \textbf{React and Next.js} applications optimized for performance, SEO, and accessibility across millions of monthly users.
  \item Drove the design and rollout of a \textbf{server-driven UI system}, reducing duplicated frontend layout logic by approximately \textbf{40\%}.
  \item Built animation-rich, interaction-heavy experiences such as the \textbf{``Name Drop''} quiz with a strong focus on UX polish and performance.
  \item Implemented frontend analytics instrumentation to support experimentation, personalization feedback loops, and product insights.
  \item Collaborated closely with design, editorial, and product teams to deliver pixel-perfect, brand-consistent user experiences.
\end{itemize}

\textbf{Technologies \& Tools}\\
React.js, Next.js, TypeScript, GraphQL, Node.js, Prisma, MongoDB, Kubernetes, Terraform, GitHub Actions, AWS, Datadog, Fastly CDN

\blockdivider

\roleheader{HTC Global Services}{Chennai, Tamil Nadu, India}{Software Developer}{Feb 2020 -- Jun 2021}
\roledivider

\projecttitle{Project: Manipal Education and Lead Management}
\begin{itemize}
  \item Built and maintained React-based administrative workflows integrated with microservice \textbf{REST APIs}, improving operational efficiency for admissions and lead teams.
  \item Designed API-driven UI modules for lead capture and tracking, ensuring robust validation, predictable state, and clean UX.
  \item Implemented serverless data ingestion pipelines using \textbf{AWS Lambda, SQS, and DynamoDB}, processing Salesforce lead data approximately \textbf{60\% faster}.
  \item Integrated \textbf{Elasticsearch} for search and reporting, enabling real-time analytics and improved lead visibility.
  \item Deployed Dockerized Node.js services on AWS EC2, improving CI/CD reliability and release stability by \textasciitilde30\%.
\end{itemize}

\textbf{Technologies \& Tools}\\
React.js, Node.js, Express.js, TypeScript, Sequelize, DynamoDB, Elasticsearch, AWS Lambda, SQS, Docker

\blockdivider

\roleheader{Develop Script LLC}{Chennai, Tamil Nadu, India}{Node JS Developer}{Dec 2018 -- Jan 2020}
\roledivider

\projecttitle{Project: Mazzady, Sothebi, PreRio, SlotCycle}
\begin{itemize}
  \item Built React-based admin and bidding interfaces with real-time updates, optimizing UI responsiveness under high concurrency.
  \item Implemented real-time auction experiences using \textbf{WebSockets (Socket.IO)} with predictable client-side state updates.
  \item Developed reusable UI patterns for bidding flows, notifications, and item detail surfaces to improve user engagement.
  \item Integrated payments, logistics, and notifications to deliver end-to-end e-commerce workflows.
\end{itemize}

\textbf{Tech Stack}\\
React.js, Node.js, Express.js, Socket.IO, Redis, AWS RDS, MySQL

% ---------- RIGHT COLUMN ----------
\switchcolumn[1]
\sideheading{Skills}

\sidesub{Frontend Engineering}
\sideitem{React.js, Next.js}
\sideitem{TypeScript, JavaScript}
\sideitem{Design Systems \& Component Architecture}
\sideitem{Server-Driven UI}
\sideitem{State Management (Redux Toolkit, React Query)}
\sideitem{Performance Optimization}
\sideitem{Accessibility (WCAG)}

\sidesub{Back-End \& APIs}
\sideitem{Node.js, Bun}
\sideitem{Express.js, Hapi}
\sideitem{REST APIs, GraphQL}
\sideitem{Apollo GraphQL, GraphQL Modules}
\sideitem{Prisma ORM, Sequelize ORM}

\sidesub{AI \& LLM Engineering}
\sideitem{Agentic AI \& Tool Calling}
\sideitem{LangChain, LangGraph}
\sideitem{RAG, Vector Databases}
\sideitem{OpenAI, LLaMA, Claude}
\sideitem{Prompt Safety \& Guardrails}

\sidesub{UI \& Tooling}
\sideitem{Tailwind CSS, Material UI}
\sideitem{Styled Components}
\sideitem{Vite, Webpack, Babel}
\sideitem{Storybook}
\sideitem{Framer Motion}

\sidesub{Testing \& Quality}
\sideitem{Playwright, Cypress}
\sideitem{Jest, Mocha, Chai}
\sideitem{Cucumber.js}
\sideitem{Vitest}

\sidesub{Data, Caching \& Search}
\sideitem{MongoDB, PostgreSQL}
\sideitem{MySQL, DynamoDB}
\sideitem{Redis}
\sideitem{Elasticsearch}

\sidesub{Cloud, DevOps \& Platform}
\sideitem{AWS (Lambda, S3)}
\sideitem{Docker, Podman}
\sideitem{Kubernetes, OpenShift}
\sideitem{Terraform}
\sideitem{Jenkins, GitHub Actions}
\sideitem{Load Balancers, CDN}

\vspace{10pt}
\sidesub{Additional Experience}
\vspace{4pt}

\sideitem{\textbf{Origin Protocol}}
\sideitem{Frontend Engineer --- Remote/Contract}
\sideitem{Dec 2020 -- Feb 2021}
\vspace{3pt}
\sideitem{Worked on an Ethereum-based dApp, implementing Web3.js and MetaMask wallet integration. Collaborated on GraphQL API extensions within a Lerna-managed monorepo.}

\vspace{8pt}
\sideitem{\textbf{Threado}}
\sideitem{Frontend Engineer --- Remote/Contract}
\sideitem{Nov 2021 -- Jan 2022}
\vspace{3pt}
\sideitem{Contributed to a community management web application using TypeScript, React, and Next.js with a component-driven UI approach.}

\vspace{8pt}
\sideitem{\textbf{Selsun Technologies}}
\sideitem{Software Trainee --- Chennai, India}
\sideitem{Dec 2017 -- Nov 2018}
\vspace{3pt}
\sideitem{Developed computer vision solutions for semi-automated equipment, enhancing OpenCV-based image processing algorithms using C++ and Python.}

\vspace{10pt}
\sideheading{Education}
\vspace{4pt}
\sideitem{\textbf{Arunai Engineering College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Bachelor of Engineering in Mechanical Engineering}
\sideitem{Aug 2013 -- Jun 2016}

\vspace{8pt}
\sideitem{\textbf{Kumaran Polytechnic College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Diploma in Mechanical Engineering}
\sideitem{Aug 2010 -- Jun 2013}

\vspace{10pt}
\sidesub{Languages}
\sideitem{ENGLISH, TAMIL, HINDI}

\vspace{10pt}
\sidesub{Social}
\sideitem{Portfolio --- \href{https://iam-hussain.site}{iam-hussain.site}}
\sideitem{LinkedIn --- \href{https://linkedin.com/in/iam-hussain}{iam-hussain}}
\sideitem{GitHub --- \href{https://github.com/iam-hussain}{iam-hussain}}

\end{paracol}

\end{document}