\documentclass[10pt,a4paper]{article}

% =========================
% PAGE SETUP (ATS SAFE)
% =========================
\usepackage[a4paper,top=0.60in,bottom=0.60in,left=0.70in,right=0.70in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[x11names,table,dvipsnames]{xcolor}

% Font (clean, ATS-friendly)
\usepackage[default]{sourcesanspro}

% Copy/paste and text extraction reliability (safe even if file missing)
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}}{}
\pdfgentounicode=1

\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{needspace}
\usepackage[none]{hyphenat}

\sloppy
\RaggedRight
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlength{\emergencystretch}{2em}

% =========================
% Minimal styling (ATS-safe)
% =========================
\definecolor{rulecolor}{HTML}{E5E7EB}

\titleformat{\section}
  {\needspace{3\baselineskip}\large\bfseries}
  {}
  {0pt}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{7pt}{4pt}

\newcommand{\divider}{\vspace{2pt}\color{rulecolor}\rule{\linewidth}{0.5pt}\color{black}\vspace{4pt}}

\setlist[itemize]{
  leftmargin=1.25em,
  itemsep=2pt,
  topsep=2pt,
  parsep=0pt
}
\renewcommand\labelitemi{\textbullet}

% =========================
% Header + Job block helpers (ATS-first)
% =========================
\newcommand{\NameSize}{\fontsize{22}{24}\selectfont}
\newcommand{\TitleSize}{\fontsize{11}{13}\selectfont}
\newcommand{\MetaSize}{\fontsize{9.6}{11.8}\selectfont}

% Strict ATS job header:
% ROLE (line 1) | DATES (right)
% COMPANY, LOCATION (line 2)
\newcommand{\job}[4]{%
\textbf{#1}\hfill #4\\
\textbf{#2}, #3\\
}

\newcommand{\project}[1]{\textit{Project: #1}\par}
\newcommand{\stack}[1]{\textit{Tech:} #1\par}

% =========================
% DOCUMENT
% =========================
\begin{document}

% =========================
% HEADER (ATS-friendly, no center needed)
% =========================
{\NameSize\bfseries Jakir Hussain}\par
{\TitleSize\bfseries Senior Full-Stack Engineer | Node.js | AI Platforms | Cloud APIs}\par
\vspace{2pt}
{\MetaSize
\href{mailto:itsjakirhussain@gmail.com}{itsjakirhussain@gmail.com}
\;|\; +971 551419969
\;|\; Dubai, UAE
\;|\; \href{https://linkedin.com/in/iam-hussain}{linkedin.com/in/iam-hussain}
\;|\; \href{https://github.com/iam-hussain}{github.com/iam-hussain}
\;|\; \href{https://iam-hussain.site}{iam-hussain.site}
\par}
\divider

% =========================
% SUMMARY
% =========================
\section*{Professional Summary}
Senior Full-Stack Engineer with 8+ years of experience building cloud-native platforms using \textbf{Node.js, TypeScript, React, and GraphQL}. Expertise in \textbf{microservices}, \textbf{REST/GraphQL API design}, \textbf{CI/CD automation}, and \textbf{AWS/Kubernetes}. Hands-on experience delivering \textbf{LLM-powered applications} including \textbf{multi-agent orchestration}, \textbf{tool calling}, and \textbf{RAG (Retrieval-Augmented Generation)} with safety guardrails for regulated enterprise use cases.

% =========================
% SKILLS (compact but keyword-rich)
% =========================
\section*{Technical Skills}
\textbf{Core:} Microservices, Distributed Systems, API Security, OAuth/OIDC, Observability, Performance Optimization, CI/CD, AWS, Kubernetes, Terraform, REST APIs, GraphQL, RAG, Tool Calling, Multi-Agent Systems\\
\textbf{Languages:} TypeScript, JavaScript, HTML, CSS\\
\textbf{Back-End:} Node.js, Bun, Express.js, Hapi, Apollo GraphQL, GraphQL Modules, Prisma ORM, Sequelize ORM\\
\textbf{Front-End:} React.js, Next.js, Redux Toolkit, React Query, React Router, Tailwind CSS, Material UI, Styled Components, Storybook, Framer Motion\\
\textbf{AI/LLM:} OpenAI API (ChatGPT), LLaMA, Claude, LangChain, LangGraph, Prompt Engineering, Guardrails, Validation\\
\textbf{Data/Search:} MongoDB, PostgreSQL, MySQL, DynamoDB, Redis, Elasticsearch\\
\textbf{Cloud/DevOps:} Docker, Kubernetes, OpenShift, Jenkins, GitHub Actions, 3Scale, Load Balancers, CDN\\
\textbf{Testing/Tools:} Playwright, Cypress, Jest, Vitest, Mocha, Chai, Cucumber.js, Datadog, Fastly CDN, Snowplow, Serverless Framework

% =========================
% EXPERIENCE (strict order)
% =========================
\section*{Work Experience}

\job{Lead - Technology}{Synechron Technologies LLC}{Dubai, UAE}{Dec 2024 -- Present}
\project{Treasury AI Assistant (Emirates NBD)}
\begin{itemize}
  \item Led development of an AI assistant for treasury users, enabling real-time insights and decision support in a regulated banking environment.
  \item Designed a \textbf{multi-agent LLM architecture} separating orchestration, domain reasoning, tool execution, and validation for traceable and auditable outputs.
  \item Defined secure prompt/tool workflows for controlled access to \textbf{Calypso APIs}, enforcing authorization and data-boundary controls.
  \item Built \textbf{RAG pipelines} using embeddings and vector search to improve answer relevance while preventing sensitive-data leakage.
  \item Added Redis-based session memory and caching to reduce latency and stabilize multi-turn user sessions.
  \item Enabled model routing across OpenAI, LLaMA, and Claude with fallback behavior and response validation guardrails.
\end{itemize}
\stack{Node.js, TypeScript, LangChain, LangGraph, OpenAI API, RAG, Redis, Calypso APIs}

\vspace{3pt}
\project{Open Finance Platform (Emirates NBD)}
\begin{itemize}
  \item Architected backend services under the UAE Central Bank Open Banking framework (Compete and Comply).
  \item Built Node.js/TypeScript microservices supporting consent-driven data exchange between LFIs and TPPs.
  \item Delivered REST and GraphQL APIs with dashboards for consent lifecycle management and regulatory workflows.
  \item Automated CI/CD using Jenkins and OpenShift, cutting deployment cycles by \textbf{~40\%}.
\end{itemize}
\stack{Node.js, TypeScript, REST, GraphQL, OpenShift, Jenkins, MongoDB, 3Scale}

\divider

\job{Software Engineer II}{Conde Nast Technology Lab}{Bangalore, India}{Jun 2021 -- Nov 2024}
\project{The New Yorker - Caption Contest and AI Personalization}
\begin{itemize}
  \item Built a full-stack personalization platform combining ML recommendations with real-time React rendering.
  \item Shipped adaptive React/Next.js experiences backed by personalization APIs, increasing engagement by \textbf{27\%}.
  \item Introduced server-driven UI patterns, reducing duplicated layout logic by \textbf{40\%} across segments and devices.
  \item Automated Kubernetes CronJobs for large-scale Instagram caption ingestion, improving synchronization and content freshness.
  \item Optimized newsletter flows and preference toggles, improving recurring sign-ups by \textbf{18\%}.
\end{itemize}
\stack{React, Next.js, TypeScript, GraphQL, Node.js, Kubernetes, Terraform, AWS, Prisma, MongoDB, MySQL}

\divider

\job{Software Developer}{HTC Global Services}{Chennai, India}{Feb 2020 -- Jun 2021}
\project{Manipal Education - Lead Management Platform}
\begin{itemize}
  \item Built microservice APIs for an online platform supporting \textbf{50K+ students}.
  \item Delivered serverless ingestion pipelines (AWS Lambda, SQS, DynamoDB), accelerating Salesforce data processing by \textbf{60\%}.
  \item Added Elasticsearch-powered search and async processing to support near real-time analytics and reporting.
  \item Containerized Node.js services and strengthened CI/CD reliability by \textbf{~30\%}.
\end{itemize}
\stack{Node.js, TypeScript, Express.js, AWS Lambda, SQS, DynamoDB, Elasticsearch, Docker}

\divider

\job{Node.js Developer}{Develop Script LLC}{Chennai, India}{Dec 2018 -- Jan 2020}
\project{E-commerce and Auction Platforms (Mazzady, Sothebi, PreRio, SlotCycle)}
\begin{itemize}
  \item Delivered real-time auction functionality using Node.js and WebSockets (Socket.IO) for live bidding.
  \item Added Redis Pub/Sub to synchronize bid events across concurrent users with low-latency updates.
  \item Built payment, logistics, and notification workflows supporting end-to-end commerce operations.
\end{itemize}
\stack{Node.js, Express.js, React.js, Socket.IO, Redis, MySQL, AWS RDS}

% =========================
% ADDITIONAL EXPERIENCE (ATS-friendly section)
% =========================
\section*{Additional Experience}

\job{Frontend Engineer (Contract)}{Origin Protocol}{Remote (San Francisco, CA)}{Dec 2020 -- Feb 2021}
\begin{itemize}
  \item Shipped functional enhancements for an Ethereum-based dApp supporting wallet-based user flows and on-chain transactions.
  \item Built MetaMask connectivity with Web3.js and improved GraphQL API interactions within a multi-package monorepo.
\end{itemize}
\stack{TypeScript, GraphQL, Web3.js, MetaMask, Lerna, Styled Components}

\job{Frontend Engineer (Contract)}{Threado}{Bangalore, India}{Nov 2021 -- Jan 2022}
\begin{itemize}
  \item Built production-ready UI features for a community management platform using TypeScript and React with Next.js routing patterns.
  \item Improved page performance and component reuse by standardizing UI patterns and state updates.
\end{itemize}
\stack{TypeScript, React, Next.js, Redux, Material UI, Styled Components}

\job{Software Trainee}{Selsun Technologies}{Chennai, India}{Dec 2017 -- Nov 2018}
\begin{itemize}
  \item Developed computer vision solutions for semi-automated equipment and refined OpenCV pipelines for image-based inspection.
  \item Improved C++ and Python image-processing modules to increase robustness under variable lighting and noisy input.
\end{itemize}
\stack{C++, Python, OpenCV}

% =========================
% EDUCATION
% =========================
\section*{Education}
\textbf{Arunai Engineering College}, Tiruvannamalai, India \hfill Aug 2013 -- Jun 2016\\
Bachelor of Engineering in Mechanical Engineering

\textbf{Kumaran Polytechnic College}, Tiruvannamalai, India \hfill Aug 2010 -- Jun 2013\\
Diploma in Mechanical Engineering

% =========================
% LANGUAGES
% =========================
\section*{Languages}
English, Tamil, Hindi

\end{document}