\documentclass[10pt,a4paper]{article}

% =========================
% ATS + 2-PAGE OPTIMIZATION
% =========================
\usepackage[a4paper,top=0.55in,bottom=0.55in,left=0.70in,right=0.70in]{geometry}

% --- Encoding / text extraction ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cmap}
\input{glyphtounicode}
\pdfgentounicode=1

% Font
\usepackage[default]{sourcesanspro}

% Core
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{needspace}
\usepackage[none]{hyphenat}

% =========================
% Typography
% =========================
\sloppy
\setlength{\emergencystretch}{2em}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\RaggedRight

% =========================
% Styling (ATS-safe)
% =========================
\definecolor{primary}{HTML}{111827}
\definecolor{secondary}{HTML}{4B5563}
\definecolor{rulecolor}{HTML}{E5E7EB}

\hypersetup{
  colorlinks=true,
  urlcolor=primary,
  linkcolor=primary
}
\urlstyle{same}

\titleformat{\section}
  {\needspace{3\baselineskip}\bfseries\color{primary}\large}
  {}
  {0pt}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{7pt}{3pt}

\newcommand{\divider}{\color{rulecolor}\rule{\linewidth}{0.45pt}\color{primary}}

% Tight lists (key for 2 pages)
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt
}
\renewcommand\labelitemi{\textbullet}

% Font hierarchy
\newcommand{\NameSize}{\fontsize{22}{24}\selectfont}
\newcommand{\TitleSize}{\fontsize{11}{13}\selectfont}
\newcommand{\MetaSize}{\fontsize{9.3}{11.2}\selectfont}

% Job format: Role / Company / Location / Dates (parser-stable)
\newcommand{\job}[4]{%
  \textbf{#1} \hfill \textcolor{secondary}{#4}\\
  \textit{#2, #3}\par
}

% Project label prevents ATS role confusion
\newcommand{\project}[1]{\textit{Project: #1}\par}

% Compact tech line
\newcommand{\stack}[1]{\textit{Tech:} #1\par}

% =========================
% DOCUMENT
% =========================
\begin{document}

% =========================
% HEADER (ATS-friendly, improved)
% =========================
{\NameSize\bfseries Jakir Hussain}\par
\vspace{2pt}

{\TitleSize\bfseries Senior Full-Stack Engineer — Node.js, AI Platforms, Cloud \& APIs}\par
\vspace{4pt}

{\MetaSize
Dubai, UAE \;|\;
\href{mailto:itsjakirhussain@gmail.com}{itsjakirhussain@gmail.com}
\;|\; +971 551419969 \par
\href{https://linkedin.com/in/iam-hussain}{linkedin.com/in/iam-hussain}
\;|\; \href{https://iam-hussain.site}{iam-hussain.site}
\;|\; \href{https://github.com/iam-hussain}{github.com/iam-hussain}
}

\vspace{6pt}
\divider
% =========================
% SUMMARY (tight)
% =========================
\section*{Professional Summary}
Senior Full-Stack Engineer with 8+ years building cloud-native platforms using \textbf{Node.js, TypeScript, React, and GraphQL}. Experienced in \textbf{microservices}, \textbf{REST/GraphQL APIs}, \textbf{CI/CD}, and \textbf{AWS/Kubernetes}. Hands-on in \textbf{LLM application development} (\textbf{multi-agent orchestration}, \textbf{tool calling}, \textbf{RAG}, \textbf{guardrails}) for secure and scalable fintech/media/regulated enterprise systems.
% =========================
% TECHNICAL SKILLS
% =========================
\section*{Technical Skills}

\textbf{Core Engineering:}  
Microservices, Distributed Systems, REST APIs, GraphQL, API Security, OAuth/OIDC, Observability, Performance Optimization, CI/CD, Cloud-Native Architecture

\textbf{Languages:}  
TypeScript, JavaScript, HTML, CSS

\textbf{Back-End:}  
Node.js, Bun, Express.js, Hapi, Apollo GraphQL, GraphQL Modules, Prisma ORM, Sequelize ORM

\textbf{Front-End:}  
React.js, Next.js, Redux Toolkit, React Query, React Router, Tailwind CSS, Material UI, Styled Components, Storybook, Framer Motion

\textbf{AI / LLM Engineering:}  
OpenAI API (ChatGPT), LLaMA, Claude, LangChain, LangGraph, Prompt Engineering, Tool Calling, RAG, Guardrails, Validation

\textbf{Data \& Search:}  
MongoDB, PostgreSQL, MySQL, DynamoDB, Redis, Elasticsearch

\textbf{Cloud \& DevOps:}  
AWS (Lambda, S3), Docker, Kubernetes, OpenShift, Terraform, Jenkins, GitHub Actions, 3Scale, Load Balancers, CDN

\textbf{Testing \& Observability:}  
Playwright, Cypress, Jest, Vitest, Mocha, Chai, Cucumber.js, Datadog, Snowplow, Fastly CDN, Serverless Framework

\textbf{Engineering Practices:}  
System Design, Security-Aware Development, Compliance, Web Accessibility (WCAG)
% =========================
% WORK EXPERIENCE
% =========================
\section*{Work Experience}

\job{Lead - Technology}{Synechron Technologies LLC}{Dubai, UAE}{Dec 2024 -- Present}
\project{Treasury AI Assistant (Emirates NBD)}
\begin{itemize}
  \item Leading delivery of an AI conversational assistant for Treasury, enabling real-time insights and decision support in a regulated environment.
  \item Architected a \textbf{multi-agent LLM system} separating orchestration, reasoning, tool execution, and validation for traceable, auditable outputs.
  \item Designed secure \textbf{prompt/tool workflows} to access \textbf{Calypso APIs} with strict authorization and data-boundary controls.
  \item Implemented \textbf{RAG} with vector search/embeddings for context-aware responses while preventing data leakage.
  \item Built \textbf{Redis session memory + caching} for low-latency retrieval and controlled lifecycle management.
  \item Integrated \textbf{OpenAI API (ChatGPT)}, LLaMA, Claude with routing/fallback and safety guardrails (masking, policy checks, validation).
\end{itemize}
\stack{Node.js, TypeScript, LangChain, LangGraph, OpenAI API, RAG, Vector DB, Redis, Calypso APIs}

\project{Open Finance Platform (Emirates NBD)}
\begin{itemize}
  \item Led backend/API architecture under UAE Central Bank Open Banking framework (Compete \& Comply).
  \item Delivered \textbf{Node.js/TypeScript microservices} for consent-driven exchange between LFIs and TPPs.
  \item Implemented \textbf{REST + GraphQL APIs} integrated with React/Next.js dashboards for regulatory workflows and consent lifecycle.
  \item Implemented \textbf{3Scale} and automated \textbf{CI/CD} (Jenkins, OpenShift), reducing release cycles by \textbf{~40\%}.
\end{itemize}
\stack{TypeScript, REST, GraphQL, 3Scale, OpenShift, Docker, Kubernetes, Jenkins, MongoDB}

\vspace{3pt}
\divider

\job{Software Engineer II}{Cond\'e Nast Technology Lab}{Bangalore, India}{Jun 2021 -- Nov 2024}
\project{The New Yorker (Caption Contest, AI Personalization, Home, Quizzes, Newsletters)}
\begin{itemize}
  \item Built a full-stack \textbf{AI personalization platform} integrating ML recommendations with real-time React rendering.
  \item Delivered adaptive \textbf{React/Next.js} experiences, increasing engagement by \textbf{27\%}.
  \item Rolled out \textbf{server-driven UI}, reducing duplicated layout logic by \textbf{40\%} across devices/segments.
  \item Automated \textbf{Kubernetes CronJobs} for Instagram caption ingestion to improve synchronization and discovery.
  \item Optimized newsletter subscription workflows, increasing recurring sign-ups by \textbf{18\%}; improved accessibility via audio playback/adaptive media.
\end{itemize}
\stack{React, Next.js, TypeScript, GraphQL, Node.js, Kubernetes, Terraform, AWS, Prisma, MongoDB, MySQL}

\vspace{3pt}
\divider

\job{Software Developer}{HTC Global Services}{Chennai, India}{Feb 2020 -- Jun 2021}
\project{Manipal Education (Lead Management Platform)}
\begin{itemize}
  \item Built microservice APIs for an online platform serving \textbf{50K+ students}.
  \item Implemented serverless ingestion (Lambda, SQS, DynamoDB), improving Salesforce processing by \textbf{60\%}.
  \item Integrated \textbf{Elasticsearch} and async event processing for real-time analytics/reporting.
  \item Deployed Dockerized Node.js services on AWS EC2, improving CI/CD reliability by \textbf{~30\%}.
\end{itemize}
\stack{Node.js, TypeScript, Express, AWS Lambda, SQS, DynamoDB, Elasticsearch, Docker}

\vspace{3pt}
\divider

\job{Node.js Developer}{Develop Script LLC}{Chennai, India}{Dec 2018 -- Jan 2020}
\project{Client Projects (Mazzady, Sothebi, PreRio, SlotCycle)}
\begin{itemize}
  \item Built real-time auction platforms using Node.js, Express, and WebSockets (Socket.IO).
  \item Implemented Redis Pub/Sub for low-latency bid synchronization across concurrent users.
  \item Integrated payments, logistics, and notifications for end-to-end e-commerce workflows.
\end{itemize}
\stack{Node.js, Express, React, Socket.IO, Redis, MySQL, AWS RDS}

% =========================
% ADDITIONAL EXPERIENCE
% =========================
\section*{Additional Experience}

\textbf{Frontend Engineer (Contract)} — Origin Protocol (Remote, San Francisco, CA)
\hfill Dec 2020 -- Feb 2021
\begin{itemize}
  \item Contributed to functional enhancements for an Ethereum-based decentralized application (dApp) supporting on-chain transactions.
  \item Integrated \textbf{Web3.js} with \textbf{MetaMask} to enable secure wallet connectivity and transaction signing.
  \item Extended \textbf{GraphQL APIs} and improved blockchain event handling in collaboration with backend engineers.
  \item Worked within a \textbf{Lerna-managed monorepo}, supporting modular frontend development and shared tooling.
\end{itemize}
\stack{TypeScript, GraphQL, Web3.js, MetaMask, Lerna, Styled Components}

\vspace{4pt}

\textbf{Frontend Engineer (Contract)} — Threado (Bangalore, India)
\hfill Nov 2021 -- Jan 2022
\begin{itemize}
  \item Contributed to the development of a community management web application in a fast-paced startup environment.
  \item Built user-facing features and pages using \textbf{TypeScript} and \textbf{React}, following component-driven design principles.
  \item Worked with \textbf{Next.js} for routing, performance optimization, and SEO-friendly rendering.
\end{itemize}
\stack{TypeScript, React, Next.js, Material UI, Styled Components, Redux}

\vspace{4pt}

\textbf{Software Trainee} — Selsun Technologies (Chennai, India)
\hfill Dec 2017 -- Nov 2018
\begin{itemize}
  \item Worked on computer vision solutions for semi-automated industrial equipment.
  \item Enhanced \textbf{OpenCV-based image processing algorithms} to improve accuracy and performance.
  \item Developed supporting utilities and algorithms using \textbf{C++} and \textbf{Python} under tight delivery timelines.
\end{itemize}
\stack{C++, Python, OpenCV}
% =========================
% EDUCATION
% =========================
\section*{Education}
\textbf{Arunai Engineering College} — Tiruvannamalai, Tamil Nadu, India \hfill Aug 2013 -- Jun 2016\\
Bachelor of Engineering in Mechanical Engineering

\textbf{Kumaran Polytechnic College} — Tiruvannamalai, Tamil Nadu, India \hfill Aug 2010 -- Jun 2013\\
Diploma in Mechanical Engineering

% =========================
% LANGUAGES
% =========================
\section*{Languages}
English, Tamil, Hindi

\end{document}