\documentclass[10pt,a4paper]{article}

% =========================
% PAGE / MARGINS (balanced for 2 pages)
% =========================
\usepackage[a4paper,top=0.45in,bottom=0.45in,left=0.45in,right=0.45in]{geometry}

% =========================
% FONTS (pdfLaTeX, no imports)
% =========================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{sourcesanspro}

% =========================
% CORE
% =========================
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{needspace}
\usepackage{paracol}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[none]{hyphenat} % prevents word hyphenation/breaking

% =========================
% COLORS
% =========================
\definecolor{primary}{HTML}{111827}
\definecolor{secondary}{HTML}{6B7280}
\definecolor{rulecolor}{HTML}{E5E7EB}

% =========================
% LINKS (ATS-safe)
% =========================
\hypersetup{
  colorlinks=true,
  linkcolor=primary,
  urlcolor=primary,
  citecolor=primary,
  pdfborder={0 0 0}
}
\urlstyle{same}

% =========================
% TYPOGRAPHY
% =========================
\setlength{\headheight}{30pt}
\setlength{\headsep}{5pt}
\setlength{\columnsep}{1.8em}
\RaggedRight
\linespread{1.03}
\setlength{\emergencystretch}{2em}
\sloppy

% =========================
% PAGE HEADER (PAGE 1 / PAGE 2)
% =========================
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\textcolor{secondary}{\footnotesize PAGE \thepage}}

% =========================
% SECTION STYLE (RIGHT COLUMN)
% =========================
\titleformat{\section}
  {\needspace{3\baselineskip}\large\bfseries\color{primary}}
  {}
  {0pt}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{0pt}{4pt}

% =========================
% LISTS
% =========================
\setlist[itemize]{leftmargin=1.15em, itemsep=2pt, topsep=3pt, parsep=0pt, partopsep=0pt}
\renewcommand\labelitemi{\textbullet}

% =========================
% SIZING HELPERS (font hierarchy)
% =========================
\newcommand{\NameSize}{\fontsize{22}{24}\selectfont}
\newcommand{\TitleSize}{\fontsize{10.8}{13}\selectfont}
\newcommand{\TagSize}{\fontsize{10}{12}\selectfont}
\newcommand{\BodySize}{\fontsize{9.7}{12}\selectfont}
\newcommand{\SmallBody}{\fontsize{9.2}{11.4}\selectfont}

% =========================
% DIVIDERS (IMPORTANT: reset to primary after rule)
% =========================
\newcommand{\topdivider}{\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{0pt}}
\newcommand{\blockdivider}{\vspace{0pt}\color{rulecolor}\rule{\linewidth}{0.5pt}\color{primary}\vspace{4pt}}

% =========================
% SIDEBAR MACROS (LEFT COLUMN)
% =========================
\newcommand{\sideheading}[1]{%
  {\RaggedRight\bfseries\color{primary}\large\MakeUppercase{#1}\par}%
  \vspace{0pt}%
}
\newcommand{\sidesub}[1]{%
  \vspace{6pt}%
  {\RaggedRight\bfseries\color{primary}\MakeUppercase{#1}\par}%
  \vspace{3pt}%
}
\newcommand{\sideitem}[1]{%
  {\RaggedRight\SmallBody\textcolor{primary}{%
    \hyphenpenalty=10000\exhyphenpenalty=10000 #1}\par}%
}

% =========================
% RIGHT COLUMN HELPERS (ATS-optimized role structure)
% =========================
% Order is intentionally: Job Title -> Company | Location -> Dates
\newcommand{\roleheader}[4]{%
  \noindent
  \textbf{\MakeUppercase{#3}}%
  \hfill
  \textcolor{secondary}{#4}\\[0pt]
  \noindent
  \textbf{#1}%
  \hfill
  \textcolor{secondary}{#2}\\[0pt]
}
\newcommand{\roledivider}{%
  \vspace{-1pt}%
  {\color{rulecolor}\rule{\linewidth}{0.5pt}}%
  \vspace{2pt}%
}
\newcommand{\projecttitle}[1]{\textbf{#1}\par\vspace{2pt}}

% =========================
% DOCUMENT
% =========================
\begin{document}
\BodySize

% =========================
% HEADER
% =========================
\begin{center}
{\NameSize \bfseries JAKIR HUSSAIN}\\[4pt]
{\TitleSize \bfseries SENIOR FULL-STACK ENGINEER}\\[2pt]
{\TagSize \bfseries NODE.JS \;|\; REACT \& NEXT.JS \;|\; CLOUD \& APIs \;|\; AI-ENABLED FEATURES}\\[6pt]

\href{mailto:itsjakirhussain@gmail.com}{itsjakirhussain@gmail.com} \;|\;
+971 551419969 \;|\;
Dubai, UAE \;|\;
\href{https://linkedin.com/in/iam-hussain}{linkedin.com/in/iam-hussain} \;|\;
\href{https://iam-hussain.site}{iam-hussain.site}
\end{center}
\vspace{-8pt}
\topdivider
\vspace{2pt}

% =========================
% SUMMARY (Full-Stack first, AI as advantage)
% =========================
\section*{Professional Summary}
\SmallBody
Senior Full-Stack Engineer with 8+ years of experience building and scaling end-to-end web platforms across frontend, backend, and cloud deployments. Strong in \textbf{React/Next.js}, \textbf{Node.js/TypeScript}, and \textbf{GraphQL/REST} with a proven track record delivering performance, reliability, and developer velocity improvements in enterprise and high-traffic consumer environments.\\[4pt]
Differentiates through applied AI capabilities: integrating \textbf{LLM-powered features}, \textbf{RAG-based knowledge access}, and \textbf{governed automation} into full-stack systems while maintaining security, observability, and compliance.

\vspace{1pt}
\topdivider
\vspace{2pt}

% ============================================================
% PAGE: LEFT = EXPERIENCE, RIGHT = SKILLS
% ============================================================
\setcolumnwidth{0.69\textwidth,0.31\textwidth}
\begin{paracol}{2}

% ---------- LEFT COLUMN ----------
\switchcolumn[0]*
\section*{Work Experience}

\roleheader{Synechron Technologies LLC (Client: Emirates NBD)}{Dubai, UAE}{Lead -- Technology}{Dec 2024 -- Present}
\roledivider

\projecttitle{Project: Open Finance Platform (UAE Open Banking)}

\begin{itemize}
  \item Owned end-to-end delivery of \textbf{full-stack Open Banking platforms}, combining \textbf{React/Next.js dashboards} with \textbf{Node.js and TypeScript microservices}.
  \item Designed and implemented \textbf{consent-driven REST and GraphQL APIs} enabling secure data exchange between LFIs and TPPs under UAE Central Bank Open Banking regulations.
  \item Led \textbf{API contract design and versioning strategy} to support backward compatibility and phased regulatory rollouts.
  \item Integrated \textbf{API gateway and policy enforcement} using \textbf{3Scale}, implementing throttling, rate limits, OAuth flows, and request validation.
  \item Built scalable backend services with \textbf{MongoDB and Redis}, optimizing data access, caching, and session management for high-throughput workflows.
  \item Implemented \textbf{role-based access control (RBAC)} and consent lifecycle management to enforce fine-grained authorization.
  \item Automated \textbf{CI/CD pipelines} using \textbf{Jenkins and OpenShift}, enabling repeatable, zero-downtime deployments across environments.
  \item Collaborated with compliance, security, and regulatory stakeholders to align platform architecture with enterprise governance, audit, and data residency standards.
\end{itemize}

\textbf{Technologies \& Tools}\\
Node.js, TypeScript, React.js, Next.js, Express.js, GraphQL, MongoDB, Redis, OpenShift, Kubernetes, 3Scale, Jenkins, Docker

\blockdivider

\projecttitle{Project: Treasury AI Assistant}
\begin{itemize}
  \item Designed and delivered an \textbf{AI-powered internal treasury assistant}, providing contextual insights, operational intelligence, and workflow automation for treasury teams.
  \item Architected \textbf{LLM-integrated backend services} that orchestrate prompt execution, tool invocation, and response validation within controlled workflows.
  \item Implemented \textbf{Retrieval-Augmented Generation (RAG)} pipelines with document ingestion, chunking, embeddings, and relevance filtering to safely query internal financial data.
  \item Developed structured \textbf{tool-calling workflows} with deterministic execution, retries, and guardrails to ensure auditability and predictable outcomes.
  \item Enforced \textbf{authorization-aware AI responses}, ensuring data access adhered to user entitlements and regulatory boundaries.
  \item Integrated \textbf{Redis-based conversational memory and caching} to maintain stateful interactions and ensure low-latency responses.
  \item Implemented monitoring and traceability for AI workflows, enabling observability into request flows, latency, and failure modes.
  \item Partnered with treasury, risk, and security teams to productionize AI workflows in a regulated banking environment.
\end{itemize}

\textbf{Technologies \& Tools}\\
Node.js, TypeScript, LLM Integrations, RAG Pipelines, Redis, Vector Databases, Internal APIs
\vspace{16pt}

\roleheader{Cond\'e Nast Technology Lab}{Bangalore, India}{Software Engineer II}{Jun 2021 -- Nov 2024}
\roledivider

\projecttitle{Project: The New Yorker (Caption Contest, AI Personalization, Home, Quizzes \& Newsletters)}
\begin{itemize}
  \item Architected and delivered a \textbf{full-stack AI-driven personalization platform}, integrating ML recommendations with real-time React rendering across high-traffic editorial surfaces.
  \item Built scalable \textbf{React and Next.js applications} backed by personalization and content APIs, increasing user engagement by \textbf{27\%}.
  \item Designed and automated \textbf{Kubernetes CronJobs} for large-scale Instagram caption ingestion and continuous content synchronization.
  \item Led the POC and production rollout of \textbf{server-driven UI}, reducing duplicated layout logic by approximately \textbf{40\%}.
  \item Developed the \textbf{``Name Drop''} quiz application end-to-end from Figma designs, combining animation-driven UX with backend logic and performance optimization.
  \item Implemented end-to-end analytics instrumentation (\textbf{Snowplow + GraphQL}) to support personalization feedback loops and experimentation.
  \item Improved application performance and reliability through targeted optimizations, code-splitting, and monitoring using \textbf{Datadog} and browser performance metrics.
\end{itemize}

\textbf{Technologies \& Tools}\\
React.js, Next.js, TypeScript, GraphQL, Node.js, Prisma, MongoDB, Kubernetes, Terraform, GitHub Actions, AWS, Datadog, Fastly CDN

\blockdivider

\roleheader{HTC Global Services}{Chennai, Tamil Nadu, India}{Software Developer}{Feb 2020 -- Jun 2021}
\roledivider

\projecttitle{Project: Manipal Education and Lead Management}
\begin{itemize}
  \item Designed and built microservice-based \textbf{REST APIs} for Manipal University’s online education platform, supporting \textbf{50K+ active students}.
  \item Implemented serverless data ingestion pipelines using \textbf{AWS Lambda, SQS, and DynamoDB}, processing Salesforce lead data approximately \textbf{60\% faster}.
  \item Integrated \textbf{Elasticsearch} for search and reporting, enabling real-time analytics and improved lead visibility.
  \item Deployed Dockerized Node.js services on AWS EC2, improving CI/CD reliability and release stability by \textasciitilde30\%.
  \item Collaborated closely with frontend teams to integrate React applications with backend services and APIs.
\end{itemize}

\textbf{Technologies \& Tools}\\
Node.js, Express.js, TypeScript, Sequelize, DynamoDB, Elasticsearch, AWS Lambda, SQS, Docker

\blockdivider

\roleheader{Develop Script LLC}{Chennai, Tamil Nadu, India}{Node JS Developer}{Dec 2018 -- Jan 2020}
\roledivider

\projecttitle{Project: Mazzady, Sothebi, PreRio, SlotCycle}
\begin{itemize}
  \item Built real-time auction platforms using \textbf{Node.js, Express, and WebSockets (Socket.IO)}.
  \item Implemented \textbf{Redis Pub/Sub} for low-latency bid synchronization across concurrent users.
  \item Integrated payments, logistics, and notifications to deliver end-to-end e-commerce workflows.
  \item Developed React-based admin and bidding interfaces with real-time updates.
\end{itemize}

\textbf{Tech Stack}\\
Node.js, Express.js, React.js, Socket.IO, Redis, AWS RDS, MySQL

% ---------- RIGHT COLUMN ----------
\switchcolumn[1]
\sideheading{Skills}

\sidesub{Back-End \& APIs}
\sideitem{Node.js, Bun}
\sideitem{TypeScript, JavaScript}
\sideitem{Express.js, Hapi}
\sideitem{REST APIs, GraphQL}
\sideitem{Apollo GraphQL, GraphQL Modules}
\sideitem{Prisma ORM, Sequelize ORM}

\sidesub{Front-End}
\sideitem{React.js, Next.js}
\sideitem{Redux Toolkit, React Query, React Router}
\sideitem{Tailwind CSS, Material UI}
\sideitem{Styled Components}
\sideitem{Vite, Webpack, Babel}
\sideitem{Storybook}
\sideitem{Framer Motion}

\sidesub{Mobile \& Desktop}
\sideitem{React Native, Expo}
\sideitem{Electron, Tauri}
\sideitem{React Native WebView}

\sidesub{AI \& LLM Engineering}
\sideitem{LLM Application Development}
\sideitem{Multi-Agent Architectures \& Tool Calling}
\sideitem{LangChain (Agents, Tools), LangGraph}
\sideitem{OpenAI (ChatGPT), LLaMA, Claude}
\sideitem{Prompt Engineering \& Safety}
\sideitem{RAG, AI Guardrails \& Validation}

\sidesub{Data, Caching \& Search}
\sideitem{MongoDB, PostgreSQL}
\sideitem{MySQL, DynamoDB}
\sideitem{Redis (Embedded \& Distributed)}
\sideitem{Elasticsearch}

\sidesub{Cloud, DevOps \& Platform}
\sideitem{AWS (Lambda, S3)}
\sideitem{Docker, Podman}
\sideitem{Kubernetes, OpenShift}
\sideitem{Terraform}
\sideitem{Jenkins, GitHub Actions}
\sideitem{Serverless Architectures}
\sideitem{Load Balancers, CDN}

\sidesub{Testing \& QA}
\sideitem{Playwright, Cypress}
\sideitem{Jest, Mocha, Chai}
\sideitem{Cucumber.js}
\sideitem{Vitest}

\vspace{16pt}

\sidesub{Engineering Practices}
\sideitem{System Design \& Architecture}
\sideitem{Microservices Architecture}
\sideitem{Performance Optimization}
\sideitem{Security-Aware Development}
\sideitem{Compliance-Driven Systems}
\sideitem{CI/CD Automation}
\sideitem{Web Accessibility (WCAG)}

\vspace{10pt}
\sidesub{Additional Experience}
\vspace{4pt}

\sideitem{\textbf{Origin Protocol}}
\sideitem{Frontend Engineer --- Remote/Contract}
\sideitem{Dec 2020 -- Feb 2021}

\vspace{3pt}
\sideitem{Worked on an Ethereum-based dApp, implementing Web3.js and MetaMask wallet integration. Collaborated on GraphQL API extensions within a Lerna-managed monorepo.}

\vspace{8pt}

\sideitem{\textbf{Threado}}
\sideitem{Frontend Engineer --- Remote/Contract}
\sideitem{Nov 2021 -- Jan 2022}

\vspace{3pt}
\sideitem{Contributed to a community management web application using TypeScript, React, and Next.js with a component-driven UI approach.}

\vspace{8pt}

\sideitem{\textbf{Selsun Technologies}}
\sideitem{Software Trainee --- Chennai, India}
\sideitem{Dec 2017 -- Nov 2018}

\vspace{3pt}
\sideitem{Developed computer vision solutions for semi-automated equipment, enhancing OpenCV-based image processing algorithms using C++ and Python.}

\vspace{10pt}

\sideheading{Education}
\vspace{4pt}
\sideitem{\textbf{Arunai Engineering College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Bachelor of Engineering in Mechanical Engineering}
\sideitem{Aug 2013 -- Jun 2016}

\vspace{8pt}
\sideitem{\textbf{Kumaran Polytechnic College}}
\sideitem{Tiruvannamalai, Tamil Nadu, India}
\vspace{3pt}
\sideitem{Diploma in Mechanical Engineering}
\sideitem{Aug 2010 -- Jun 2013}

\vspace{10pt}
\sidesub{Languages}
\sideitem{ENGLISH, TAMIL, HINDI}

\vspace{10pt}
\sidesub{Social}

\sideitem{Portfolio --- \href{https://iam-hussain.site}{iam-hussain.site}}
\sideitem{LinkedIn --- \href{https://linkedin.com/in/iam-hussain}{iam-hussain}}
\sideitem{GitHub --- \href{https://github.com/iam-hussain}{iam-hussain}}

\end{paracol}

\end{document}